---
title: "Stock Data App"
author: "Raviraj Chittaranjan"
date: "November 5, 2016"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Stock Data App Introduction

- The main purpose of this application is to allow users to interactively gain insight about major stocks sold on various stock markets in the US. 
- The data for this app is downloaded from Quandl.com. 
- This application has 2 tabs which present the stock data in Interactive charts.

The application is available at https://mayuriravi.shinyapps.io/DSC-Assignment4/

## Application Features

- About tab
 --    Lists the features available as par of the application
- Linear Model tab
 --   An Interactive plot with a dynamic Linear Model line based on user selected data points
- Selective Graph tab
 --   An Intractive plot with data refreshed based on the selections from the drop down

## Linear Model
An Interactive chart that displays Linear model
```{r, echo = FALSE, include=FALSE}
library(shiny)
library(plotly)
```

```{r,echo = FALSE}
mydata <- read.csv("stocksdata.csv")
plot(mydata$comm_shares_out, mydata$oper_income, xlab = "Common Outstanding Shares(Thousands)",
         ylab = "Operating Income", main = "Company Performance(Thousands)",
             cex = 1.5, pch = 16, bty = "n", col = "dark red")
p  <- lm(oper_income ~ comm_shares_out, data = mydata)
abline(p, col = "blue", lwd = 2)
```

## Selective Graph
This chart provides a sample output for Company APPLE and fiscal year 2016
```{r, echo = FALSE}
subdata <- mydata[mydata$comp_name == "APPLE INC" & mydata$per_fisc_year == 2016 & mydata$per_type == "Q",]
plot(x = subdata$per_fisc_qtr, y = subdata$pre_tax_income, type="l", xlab = "Quarters",
                    ylab = "Pre Tax Income(Thousands)", main = "Company Pre Tax Income over various quarters for the selected year", cex = 1.5, pch = 16, col = "dark red")

```

